The Impact of the 2022-23 NBA Rule Change

### 2024-04-21 paper/paper.qmd
Update paper, README, models

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

#analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

#analysis_data |> 
#  ggplot(aes(x = width, y = length)) +
#  geom_point(alpha = 0.8) +
#  theme_minimal() +
#  labs(x = "Wing width (mm)",
#       y = "Wing length (mm)")
```

@@

@@

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

@@

```{r}
#| label: fig-points
#| fig-cap: Number of MVP points won by each player from the top 10 rankings in the 2021-22 and 2022-23 seasons
#| fig.width: 8 
#| echo: false
#| warning: false
#| message: false

@@

see (@fig-percentage)

>>>>

@@

## Data Visualization
### The distribution of MVP points won by top 10 players in the 2021-22 and 2022-23 seasons
```{r}
#| label: fig-points
#| fig-cap: Number of MVP points won by each player from the top 10 rankings in the 2021-22 and 2022-23 seasons
#| fig.width: 8 
#| echo: false
#| warning: false
#| message: false

### Different shooting performances by top 10 players in the 2021-22 and 2022-23 seasons
```{r}
#| echo: false
#| warning: false
#| message: false

@@

model2023 <-
  readRDS(file = "../models/model2023.rds")

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Summary of the model results"
#| warning: false

# Create a data frame containing the model summary information
model_summary <- tibble(
  "Variable" = c("(Intercept)", "field_goal_percentage", "three_points_percentage", "free_throw_percentage"),
  "Estimate" = c(-4628, 7399, 7410, -1640),
  "Std. Error" = c(2004, 1994, 3740, 1417),
  "t value" = c(-2.310, 3.712, 1.981, -1.158),
  "Pr(>|t|)" = c(0.06028, 0.00995, 0.09485, 0.29093)
)

# Convert the data frame to a modelsummary table
summary_table <- modelsummary(model_summary)

summary_table

@@

```{r}
#| label: fig-modelresults
#| fig-cap: "Observed vs. predicted values of MVP points won"
#| fig.height: 10
#| fig.width: 8 
#| echo: false
#| warning: false
#| message: false

# Diagnostic plots
par(mfrow = c(2, 2))  # Arrange plots in a 2x2 grid
plot(model2023)  # Generate plots

# Create a data frame of observed vs. predicted values
predicted_values <- data.frame(Observed = analyzed_data2023$points_won, 
                               Predicted = predict(model2023))

# Plot observed vs. predicted values
ggplot(predicted_values, aes(x = Observed, y = Predicted)) +
  geom_point() +
  geom_abline(color = "red", linetype = "dashed") +  # Line x=y for reference
  labs(title = "Observed vs. Predicted MVP Voting Points",
       x = "Observed Points",
       y = "Predicted Points") +
  theme_minimal()
```
